Cover Letter

### 2023-10-21 manuscript/manuscript.qmd
Update

![PRISMA flow diagram. PRISMA, Preferred Reporting Items for Systematic reviews and Meta-Analyses](prisma.jpeg){#fig-prisma}

@@

![Maternal death: Corticosteroids vs placebo or no treatment](fig2.jpg){#fig-md}

@@

![Acute pulmonary edema: Corticosteroids vs placebo or no treatment](fig3.jpg){#fig-pe}

@@

![Acute renal failure: Corticosteroids vs placebo or no treatment](fig4.jpg){#fig-rf}

>>>>

![PRISMA flow diagram. PRISMA, Preferred Reporting Items for Systematic reviews and Meta-Analyses](images/fig1.jpeg){#fig-prisma}

@@

![Maternal death: Corticosteroids vs placebo or no treatment](images/fig2.jpg){#fig-md}

@@

![Acute pulmonary edema: Corticosteroids vs placebo or no treatment](images/fig3.jpg){#fig-pe}

@@

![Acute renal failure: Corticosteroids vs placebo or no treatment](images/fig4.jpg){#fig-rf}
